
\chapter*{General Introduction}
\markboth{General Introduction}{} %pour afficher l'entete
\addcontentsline{toc}{chapter}{General Introduction}

\begin{large}
Throughout history and, across cultures communication has always played a role in human life. From times when people carved messages on stone tablets to today's era of global connectivity the need to communicate has remained constant. The evolution of communication technologies from the telegraph to \textbf{5G} networks has not made it easier to connect with others but has also driven innovation and progress pushing human civilization forward in terms of knowledge and connection. The telecommunications sector sees millions of dollars exchanged daily making it a fertile ground for investment and economic growth due to its demand and rapid technological advancements. Governments worldwide implement frameworks of regulation to ensure fairness, efficiency and equal access for all parties involved in telecommunications. These regulations aim to maintain the integrity of the telecommunications ecosystem and protect the rights of consumers, as industry players. In this changing landscape where innovation meets necessity, regulations serve as pillars of stability and fairness guaranteeing that connectivity continues to benefit societies by empowering them.


\vspace{0.5cm}

Being a student of computer science driven by a passion to facilitate the life of  every day's users I have been given an amazing opportunity. With a commitment to fairness, my task is to create a mobile application that will act as a bridge of information seamlessly connecting customers with the intricate world of telecommunications in their country. This noble mission aims to empower users by providing insights into networks and telecommunication  services fostering relationships, among all involved parties. Through the development of this app my goal is to close the divide ensuring that every user possesses the knowledge and tools to navigate the digital landscape confidently and clearly.


\vspace{0.5cm}

This report is composed from  four chapters in which , I demonstrate the whole process that I went through to realise this project:



\begin{itemize}
    \item The first chapter \textbf{"Preliminary Study"}: In this chapter I will present the host firm ,cover the  general frame of the project  and its functional and non-functional requirements , also it will contain the explanation of some terminologies used through the whole project , beside the chosen project management approach , a demonstration of the software arsenal used along the project and lastly the implemented architecture .
\end{itemize}

% \vspace{0.5cm}

\begin{itemize}
    \item The second chapter "" Mobile Application Development: The third and fourth chapter dive into the meticulous creation and implementation of the mobile application. Through iterative development, we detail each sprint's progress, covering facets of user interface, user experience, backend integration, and testing.
\end{itemize}


% \vspace{0.5cm}


This journey showcases the synergy of innovation and execution, demonstrating the potential of digital solutions in enhancing event engagement. With a focus on user-centered design and agile development, we're proud to present a solution that bridges the gap between event organizers and enthusiasts, ushering in a new era of seamless event experiences.


\end{large}









